### 2021-03-31 Chapter-3/Chapter-3.tex
Updates from Overleaf

\section{Side-channel Leakages}
\subsection{Secret-dependent Control Flow Transfers}
\begin{figure}[h]
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
void example1(uint8_t k, uint32_t m) {
  uint32_t b = (k & m) >> 7;
  if (b) {
    printf("branch 1\n");
  } else {
    printf("branch 2\n");
  }
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
push  ebp
mov   ebp, esp
movzx eax, [addr_key]    
and   eax, [addr_message] 
shr   eax, 0x7           
test  eax, eax
jne   branch 2
...
\end{lstlisting}
\end{minipage}

\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
int example6(uint16_t k) {
  int res;
  if (k > 8) {
    res = 0;
  } else {
    res = 1;
  }
  return res;
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
xor   eax, eax
cmp   [addr_k], 8
setbe  al
xor    edx, edx
ret
\end{lstlisting}
\end{minipage}
\caption{A Serious Leakage}\label{fig:chapter3:cf}
\end{figure}

\subsection{Secret-dependent Data Accesses}

>>>>

\section{Side-channel Leakages}
This section discusses two types of side-channel leakage code patterns. The key intuition is that the target application shows different control flows or data flows when it processes different sensitive input data. We refer them as secret-dependent control flow transfers and secret-dependent data accesses. Unlike previous work, our tool works on the machine code, which can provide us more prevision than the previous tools.
\subsection{Control Flow}
\begin{figure}[h]
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
int example1(uint8_t k, uint32_t m) {
  uint32_t b = (k & m) >> 7;
  if (b) {
    ...    // Branch 1
  } else {
    ...    // Branch 2
  }
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
push  ebp
mov   ebp, esp
movzx eax, [addr_key]    
and   eax, [addr_message] 
shr   eax, 0x7           
test  eax, eax
jne   branch 2
...
\end{lstlisting}
\end{minipage}\caption*{(a)}

\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
int example2(uint16_t k) {
  int res;
  if (k > 8) {
    res = 0;
  } else {
    res = 1;
  }
  return res;
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
xor   eax, eax
cmp   [addr_k], 8
setbe  al
xor    edx, edx
ret
\end{lstlisting}
\end{minipage}\caption*{(b)}
\caption{Secret-dependent Control-flow Transfers}\label{fig:chapter3:cf}
\end{figure}

\subsection{Data Flow}
\begin{figure}[h]
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t T[128];
...
int example3(uint8_t secret){
  uint32_t index = 0;
  index = (index + secret) % 128;
  uint8_t t = T[index];
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
...
lea    edx, [addr_T]
mov    eax, [addr_secret]
and    eax, 0x7f
movzx  eax, [addr_T + eax*1]
...
\end{lstlisting}
\end{minipage}\caption*{(a)}

\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t T[128];
...
int example4(uint8_t secret){
  uint32_t index = 0;
  index = (index + secret) % 128;
  uint8_t t = T[index % 4];
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
...
lea    edx, [addr_T]
mov    eax, [addr_secret]
and    eax, 0x3
movzx  eax, [addr_T + eax*1]
...
\end{lstlisting}
\end{minipage}\caption*{(b)}
\caption{Secret-dependent Data Accesses}\label{fig:chapter3:da}
\end{figure}
